Probabilistic Catalogs for Crowded Stellar Fields

### 2012-11-20 paper/ms.tex
Words in sex_N caption

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{Figures/sex_N.eps}
\end{center}
\caption{The number of stars in the catalogs produced by \sex. The true numbers
of stars shown in these plots are$\sim$82\% of the values listed in
Figure~\ref{tab:truth} because here we only count those stars with positions
in $[-1, 1] \times [-1, 1]$.
\label{fig:sex_N}}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{Figures/sex_N.eps}
\end{center}
\caption{The number of stars in the catalogs produced by \sex~compared with the
actual number of stars in the images. \sex~finds only a small fraction of the
stars actually present. This is to be expected in the high-$\sigma$ case as
\sex~then only searches for stars above a certain flux, but at the low-$\sigma$
end the number of stars is still drastically underestimated. Note that the true
numbers
of stars shown in these plots are$\sim$82\% of the values listed in
Figure~\ref{tab:truth} because here we only count those stars with positions
in $[-1, 1] \times [-1, 1]$.
\label{fig:sex_N}}
\end{figure}
